Insurance choice, decision assistance, and insurer steering

### 2021-03-24 finals/lunch-and-learn/lunch-learn-202103.Rmd
update readme and add presentation link

# Two motivating facts:

@@

>>>>

# Decisions are hard

<iframe width="560" height="315" src="https://www.youtube.com/embed/oWXNf3JVWpI?start=146" frameborder="0" allowfullscreen></iframe>

---
# In the health insurance setting...

@@

---
# What are the exchanges?

- Online marketplace to purchase private health insurance for those without insurance through their employers or other public programs

- Intended to help fill the "coverage gap" for the 40+ million uninsured individuals in the U.S. (pre ACA)

- Complicated program with various premium and cost-sharing subsidies, specific to a household

---
# Metal tiers

.pull-left[
To help with this complex decision, plans organized around tiers based on actuarial value
]

--

.pull.right[
  ![:scale 50%](metal_tiers.jpg)
]

---
# Rating areas

.pull-left[
Insurers limited in ability to adjust premiums

- Smoking
- Age
- Rating area
]

--

.pull-right[
  ![:scale 100%](CA_Rating_Regions2.jpg)
]
